---
title: "Database Setup"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_float: yes
  html_notebook:
    toc: yes
    toc_float: yes
---

The goal of htis notebook is to setup an SQL light database to house water level data. We are utilizing the [ODM2 database structure](http://www.odm2.org/) and the [rodm2 package](https://khondula.github.io/rodm2/). 

#Step 1: Create ODM2 Database
First, we need to setup our workspace and configure an SQLight file for the ODM2 database structure!
```{r setup, warning = FALSE, message = FALSE, results='hide'}

#Define working dir
working_dir<-"//nfs/palmer-group-data/Choptank/Nate/PT_Data/"

#Download rodm2 package (note, this may take a few minutes!)
library(devtools)
devtools::install_github("khondula/rodm2")
library(rodm2)
library(RSQLite)
library(DBI)
source("db_get_water_level_ts.R")

#Create SQLight databse (only do this once)
db <- create_sqlite(dir = working_dir, connect = T)
```

#Step 2: Configure database for our study sites

##2.1 Describe Equipment
Use the [db_describe_equipment](https://khondula.github.io/rodm2/reference/db_describe_equipment.html) function to insert pressure transducer information into the databse. 

Below is the equipment infromation and the wrapper function used to import it into the databse.  
```{r equipment-table, echo=F}
equipment<-read.csv(paste0(working_dir,"Database Information/equipment.csv"))
equipment
```

```{r equipment-describe, warning = FALSE, message = FALSE, results='hide'}
#Create wrapper function for the db_describe_equipment
fun<-function(n){db_describe_equipment(db, 
                    equip_name    =   as.character(equipment$serial_no[n]), 
                    serial_no     =   equipment$serial_no[n],
                    model_name    =   "U20 Pressure Transducer",
                    vendor        =   "Onset",
                    manufacturer  =   "HOBO",
                    equipment_type=   "pressureTransducer",
                    owner_first   =   "Margaret",
                    owner_last    =   "Palmer",
                    owner_email   =   "mpalmer@sesync.org")}
  
#intiate function
lapply(seq(1, length(equipment[,1])), fun)
```

##2.2 Describe Sites
Use the [db_describe_site](https://khondula.github.io/rodm2/reference/db_describe_site.html) function to insert pressure transducer sites into the database. 

Below is the site information and wrapper function used to import it into the database. 
```{r sites-table, echo=F}
sites<-read.csv(paste0(working_dir,"Database Information/sites.csv"))
sites
```

```{r sites-describe, warning = FALSE, message = FALSE, results='hide'}
#Create wrapper function for the db_describe_equipment
fun<-function(n){db_describe_site(db, site_code = sites$site_code[n])}
  
#Inititate function
lapply(seq(1, length(sites[,1])), fun)
```

##2.3 Describe Method
Use the [db_describe_method](https://khondula.github.io/rodm2/reference/db_describe_method.html) function to describe pressure transducer deployment method. Note, we are using the "[Instrument deployment](http://vocabulary.odm2.org/methodtype/InstrumentDeployment/)" method from the controlled vocabulary. Atleast inititially, this makes life easier interfacing with the structure of rodm2. 

```{r method-table, warning = FALSE, message = FALSE, results='hide'}
#Create wrapper function for the db_describe_equipment
db_describe_method(db, 
                   methodname = "PT Data Download",
                   methodcode =  "PT_Download",
                   methodtypecv = "dataRetrieval")
```

##2.3 Describe Variables
Use the [db_describe_variable](https://khondula.github.io/rodm2/reference/db_describe_variable.html) function to describe variables that are going to be included in the database.

```{r variable-describe, warning = FALSE, message = FALSE, results='hide'}
#Barometric Pressure (from baro logger)
db_describe_variable(db, 
                     variabletypecv = "Hydrology",
                     variablecode   = "barometricPressure",
                     variablenamecv = "barometricPressure")

#Absolute Pressure
db_describe_variable(db, 
                     variabletypecv = "Hydrology",
                     variablecode   = "pressureAbsolute",
                     variablenamecv = "pressureAbsolute")

#Gage Pressure
db_describe_variable(db, 
                     variabletypecv = "Hydrology",
                     variablecode   = "pressureGauge",
                     variablenamecv = "pressureGauge")

#Water Collumn Depth 
db_describe_variable(db, 
                     variabletypecv = "Hydrology",
                     variablecode   = "gageHeight",
                     variablenamecv = "gageHeight")

#Offset (to correct water level to water depth)
db_describe_variable(db, 
                     variabletypecv = "Hydrology",
                     variablecode   = "offset",
                     variablenamecv = "offset")

#Water Depth (ground surface = 0, positive values indicate inundation)
db_describe_variable(db, 
                     variabletypecv = "Hydrology",
                     variablecode   = "waterLevel",
                     variablenamecv = "waterLevel")
```

#Step 3: Go collect data!
Now that the database is setup, go collect you some emperical data!!!!

Note, there are upcoming worksheets that describe how to insert data into the database. 

```{r disconnet, warning = FALSE, message = FALSE, results='hide'}
#Disconnect from the database
RSQLite::dbDisconnect(db)
```
