---
title: "Pressure transducer workflow"
output: html_notebook
editor_options: 
  chunk_output_type: inline
chunk_output_type: console
---
  
```{r}
devtools::install_github("khondula/rodm2")
library(rodm2)
library(readr)
```

# baro and pt time series

```{r}
pt <-data.frame(
  Timestamp = c("2018-06-27 13:45:00", "2018-06-27 13:55:00"),
  "pressure" = c(10,20),
  "temp" = c(1, 15))

baro <-data.frame(
  Timestamp = c("2018-06-27 13:45:00", "2018-06-27 13:55:00"),
  "pressure" = c(100,200),
  "temp" = c(10, 150))
```

# describe barologger and pt methods

```{r}
db <- rodm2::create_sqlite(connect = TRUE)
```

```{r}
db_describe_method(db, 
                   methodname = "pt", 
                   methodcode = "pt",
                   methodtypecv = "Instrument deployment",
                   methoddescription = "pressure transducer")

db_describe_method(db, 
                   methodname = "baro", 
                   methodcode = "baro",
                   methodtypecv = "Instrument deployment",
                   methoddescription = "barometric logger")
```

# insert baro ts

to see the options for sampled medium
```{r}
get_cv_terms("medium")
```

Make sure to use names (`column =` and `units =`) in varables list!
  
```{r}
rodm2::db_insert_results_ts(db = db,
                            datavalues = baro,
                            method = "baro",
                            site_code = "QB",
                            processinglevel = "Raw data",
                            sampledmedium = "Liquid aqueous", # from controlled vocab
                            # actionby = "Nate",
                            # equipment_name = "Sensor01",
                            variables = list( # variable name CV term = list("colname", units = "CV units")
                              "Pressure" = list(column = "pressure", units = "Kilopascal"),
                              "Temperature" = list(column = "temp", units = "Degree Celsius"))
)
```


# insert pt ts

processing level = raw
method = pt

Make sure to use names (`column =` and `units =`) in vars list!
  
```{r}
rodm2::db_insert_results_ts(db = db,
                            datavalues = pt,
                            method = "pt",
                            site_code = "QB",
                            processinglevel = "Raw data",
                            sampledmedium = "Liquid aqueous",
                            # actionby = "Nate",
                            # equipment_name = "Sensor01",
                            variables = list( # CV term = list("colname", units = "CV units")
                              "Pressure" = list(column = "pressure", units = "Kilopascal"),
                              "Temperature" = list(column = "temp", units = "Degree Celsius"))
)
```

# query time series


```{r}
dbGetQuery(db, "SELECT * from Results where resulttypecv = 'Time series coverage'")
dbGetQuery(db, "SELECT * from samplingfeatures")
dbGetQuery(db, "SELECT * from featureactions")
```

```{r}
dbGetQuery(db, "select * from featureactions")
dbGetQuery(db, "select * from actions") #action begindatetime, enddatetime, actiontypecv
# methodcode from methods
# samplingfeature from featureaction
```

join with variables, units, feature action (site) info

# retrieve time series based on a result ID

Get time series values based on a result ID

```{r}
# dbListTables(db)
# dbGetQuery(db, "SELECT * from TimeSeriesResultValues")
dbGetQuery(db, "SELECT * from TimeSeriesResultValues WHERE ResultID = '1'")
```

# describe water depth method

only need to to describe function for the first time inserting data of that type 

```{r}
db_describe_method(db, methodname = "waterdepth", methodcode = "waterdepth",
                   methodtypecv = "Derivation",
                   methoddescription = "Calculate water depth from baro and pt")
```

method = waterdepth
methodtypecv = derivation

# insert water depth ts

processinglevel = derived
method = waterdepth

```{r}
wd <-data.frame(
  Timestamp = c("2018-06-27 13:45:00", "2018-06-27 13:55:00"),
  "wd" = c(1,2))
```


```{r}
library(magrittr)
db_insert_results_ts(db = db,
                     datavalues = wd,
                     method = "waterdepth",
                     site_code = "QB",
                     processinglevel = "Derived product",
                     sampledmedium = "Liquid aqueous",
                     # actionby = "Nate",
                     # equipment_name = "Sensor01",
                     variables = list( # CV term = list("colname", units = "CV units")
                       "Water depth" = list(column = "wd", units = "Meter")))
```

Now see time series in database

```{r}
dbGetQuery(db, "SELECT * from Results WHERE resulttypecv = 'Time series coverage'")
```




